---
title: "Task `r params$task`"
output: html_document
params:
  task: "2024-01-04_test"
  files: NULL
---

```{r, include = FALSE}
suppressWarnings(suppressMessages(library(knitr)))
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      results = FALSE)
suppressWarnings(suppressMessages(library(dplyr)))
suppressWarnings(suppressMessages(library(ggplot2)))
suppressWarnings(suppressMessages(library(stringr)))
suppressWarnings(suppressMessages(library(tidyr)))
suppressWarnings(suppressMessages(library(kableExtra)))
source(file = file.path("report",
                        "functions",
                        "report_helpers.R"))
```




```{r initial_settings}
task_path <- file.path("output",
                       params$task)
# task_path <- file.path("output",
#                        task)
# res <- readResults(files, all_files = FALSE)
if (!is.null(params$files)) {
  res <- readResults(params$files, all_files = FALSE)
} else {
  res <- readResults(task_path, all_files = TRUE)
}
```

## Comparisons

```{r, results = TRUE}
comps <- res %>% select(file, formula)
kableExtra::kable(comps) %>% 
  kable_paper()
```

```{r, results = TRUE}
train_res <- fitSummaryReal(res, train = TRUE)
index <- table(train_res$criteria$file)
```

## Training data results

### Order based on criteria

Order of the fits according to LPPD, mean RMSE and mean KS-test. Means have been calculated over estimates calculated from the posterior predictive samples.

```{r, results = TRUE}

fit_order <- train_res$criteria %>%
  filter(stat == "mean") %>% 
  arrange(desc(lppd),
          desc(rmse),
          desc(ks_test)) %>% 
  select(!stat)

kableExtra::kable(fit_order,
             digits = 2) %>% 
  kable_paper()
```

### Criteria
```{r, results = TRUE}
kableExtra::kable(train_res$criteria %>% select(!file),
                  digits = 2) %>% 
  pack_rows(index = index) %>% 
  kable_paper()
```

### Bayesian p-values
```{r, results = TRUE}
kableExtra::kable(train_res$bayesian_p %>% select(!file),
                  digits = 2) %>% 
  pack_rows(index = index) %>% 
  kable_paper()
```

### Descriptive statistics of the posterior predictive samples
```{r, results = TRUE}
kableExtra::kable(train_res$postpred_desc %>% select(!file),
                  digits = 2) %>% 
  pack_rows(index = index) %>% 
  kable_paper()
```

### Data set descriptives
```{r, results = TRUE}
kableExtra::kable(train_res$data_desc,
                  digits = 2) %>%
  kable_paper()
```

## Validation data results

```{r}
valid_res <- fitSummaryReal(res, train = FALSE)
index <- table(valid_res$criteria$file)
```

### Order based on criteria

Order of the fits according to LPPD, mean RMSE and mean KS-test. Means have been calculated over estimates calculated from the posterior predictive samples.

```{r, results = TRUE}
fit_order <- valid_res$criteria %>%
  filter(stat == "mean") %>% 
  arrange(desc(lppd),
          desc(rmse),
          desc(ks_test)) %>% 
  select(!stat)

kableExtra::kable(fit_order,
             digits = 2) %>% 
  kable_paper()
```

### Criteria

```{r, results = TRUE}
kableExtra::kable(valid_res$criteria %>% select(!file),
                  digits = 2) %>% 
  pack_rows(index = index) %>% 
  kable_paper()
```

### Bayesian p-values
```{r, results = TRUE}
kableExtra::kable(valid_res$bayesian_p %>% select(!file),
                  digits = 2) %>% 
  pack_rows(index = index) %>% 
  kable_paper()
```

### Descriptive statistics of the posterior predictive samples
```{r, results = TRUE}
kableExtra::kable(valid_res$postpred_desc %>% select(!file),
                  digits = 2) %>% 
  pack_rows(index = index) %>% 
  kable_paper()
```

### Data set descriptives
```{r, results = TRUE}
kableExtra::kable(valid_res$data_desc,
                  digits = 2) %>%
  kable_paper()
```
